Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
+ our HSCC'17 paper in the related work

>>>>

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants.  While
they also make use of a CEGIS-based technique, their approach is
restricted to synthesising controllers for hybrid closed-loop systems
that are stable and only consider transfer function models.  In contrast,
in the current paper we consider a state-space
representation of the physical system and synthesise controllers that
make the closed-loop system safe.  Moreover, 
a key aspect of our approach
is the fact that we integrate abstraction
refinement inside the CEGIS loop.
